Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys

### 2023-07-21 analysis/analysis.qmd
model for floating bars vs wide bars

coefs_zoom %>%
  mutate(
    term = ifelse(term=="(Intercept)", "Intercept", term),
    p.value = ifelse(p.value<0.0001, "< 0.0001", sprintf("%.4f", p.value))
  ) %>%
  gt() %>%
  tab_header("Estimates for logistic regression on zooming behavior") %>%
  cols_label(
    std.error = "SE",
    statistic = "t-statistic",
    p.value = "p-value"
  ) %>%
  fmt_number(
    columns = c(estimate, std.error),
    decimals = 2
  ) %>%
  fmt_number(
    columns = statistic,
    decimals = 1
  ) %>%
  cols_align(
    columns = p.value,
    align = "right"
  )

@@

```{r m35-summary}

>>>>

coefs_zoom$term <- c("$$\\hat{\\mu}$$", "They are the same $$\\widehat{\\rho}_{2}$$", 
                     "Wrong $$\\widehat{\\rho}_{3}$$", "Aligned $$\\widehat{\\tau}_{2}$$", 
                     "Horizontal wide $$\\widehat{\\delta}_{2}$$", "Vertical $$\\widehat{\\delta}_{3}$$")

coefs_zoom %>%
  mutate(
#    term = ifelse(term=="(Intercept)", "Intercept", term),
    p.value = ifelse(p.value<0.0001, "< 0.0001", sprintf("%.4f", p.value))
  ) %>%
  gt() %>%
  tab_header("Estimates for logistic regression on zooming behavior") %>%
  cols_label(
    std.error = "SE",
    statistic = "t-statistic",
    p.value = "p-value"
  ) %>%
  fmt_number(
    columns = c(estimate, std.error),
    decimals = 2
  ) %>%
  fmt_number(
    columns = statistic,
    decimals = 1
  ) %>%
  cols_align(
    columns = p.value,
    align = "right"
  )

@@

```{r m35-summary}
#| label: tbl-floating
#| tbl-cap: "Percentage of accuracy of responses by design."
coefs_35 <- coefs_35_notwrong %>% mutate(
  level = c("correct or same | wrong")
) %>% rbind(
coefs_35_correct %>% mutate(
  level = c("correct | same or wrong")
))

coefs_35 %>% 
  mutate(
    ci_low = estimate - 1.96*std.error,
    ci_high = estimate + 1.96*std.error,
    estimate = inv_logit(estimate),
    ci_low = inv_logit(ci_low),
    ci_high = inv_logit(ci_high),
    perc_ci = sprintf(" %.2f [%.2f, %.2f]", estimate, ci_low, ci_high)
    # perc_ci = sprintf(" %.2f [%.2f, %.2f] %s", estimate, ci_low, ci_high,
    #                    ifelse(p.value < 0.001, "***",
    #                      ifelse(p.value < 0.01, "**",
    #                        ifelse(p.value < 0.05, "*",
    #                          ifelse(p.value < 0.1, ".", " ")))))
  ) %>% 
  dplyr::select(level, task, perc_ci) %>%
  pivot_wider(names_from="task", values_from="perc_ci") %>%
  gt() %>%
  tab_header("Estimated percentage of responses [95% CI]") %>%
  cols_label(
    "level" = " "
  )
```
